Cover Letter: Cudele (Paper 306)

### 2018-02-22 paper/sections/1_introduction.tex
paper: camera ready template and squeeze to 10 pgs
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[tb] \centering
\includegraphics[width=0.35\textwidth]{figures/subtree-policies1.png}
\caption{Illustration of subtrees with different semantics co-existing in a
global namespace.  For performance, clients \oldcomment{can} relax consistency/durability on their
subtree ({\it e.g.}, HDFS) or decouple the subtree and move it locally ({\it e.g.}, BatchFS, RAMDisk).
}\label{fig:subtree-policies} \end{figure}

>>>>

\begin{figure}[tb] \centering
\includegraphics[width=0.35\textwidth]{figures/subtree-policies1.png}
\caption{Illustration of subtrees with different semantics co-existing in a
global namespace.  For performance, clients \oldcomment{can} relax consistency/durability on their
subtree ({\it e.g.}, HDFS) or decouple the subtree and move it locally ({\it e.g.}, BatchFS, RAMDisk).\vspace{-3ex}
}\label{fig:subtree-policies} \end{figure}

### 2018-02-22 paper/sections/2_related_work.tex
paper: camera ready template and squeeze to 10 pgs
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% General
The bottlenecks associated with accessing POSIX IO file system metadata are not
limited to HPC workloads and the same challenges that plagued these systems for
years are finding their way into the cloud. Workloads that deal with many small
files ({\it e.g.}, log processing and database
queries~\cite{thusoo:sigmod2010-facebook-infrastructure}) and large numbers of
simultaneous clients ({\it e.g.}, MapReduce
jobs~\cite{mckusick:acm2010-gfs-evolution}), are subject to the scalability of
the metadata service. The biggest challenge is that whenever a file is touched
the client must access the file's metadata and maintaining a file system
namespace imposes small, frequent accesses on the underlying storage
system~\cite{roselli:atec2000-FS-workloads}.  Unfortunately, scaling file
system metadata is a well-known problem and solutions for scaling data IO do
not work for metadata IO~\cite{roselli:atec2000-FS-workloads,
abad:ucc2012-mimesis, alam:pdsw2011-metadata-scaling, weil:osdi2006-ceph}. 

@@

% Non POSIX IO
High performance computing has unique requirements for file systems ({\it
e.g.}, fast creates) and well-defined workloads ({\it e.g.}, workflows) that
make relaxing POSIX IO sensible.  BatchFS assumes the application coordinates
accesses to the namespace, so the clients can batch local operations and merge
with a global namespace image lazily. Similarly, DeltaFS eliminates RPC
traffic using subtree snapshots for non-conflicting workloads and middleware
for conflicting workloads. MarFS gives users the ability to lock
``project directories" and allocate GPFS clusters for demanding metadata
workloads. TwoTiers eliminates high-latencies by storing metadata in a flash
tier; applications lock the namespace so that metadata can be accessed more quickly.
Unfortunately, decoupling the namespace has costs: (1) merging metadata state
back into the global namespace is slow; (2) failures are local to the failing
node; and (3) the systems are not backwards compatible.

@@

For (1), state-of-the-art systems manage consistency in non-traditional ways:
IndexFS maintains the global namespace but blocks operations from other clients
until the first client drops the lease, BatchFS does operations on a snapshot
of the namespace and merges batches of operations into the global namespace,
and DeltaFS never merges back into the global namespace. The merging for
BatchFS is done by an auxiliary metadata server running on the client and
conflicts are resolved by the application. Although DeltaFS never explicitly
merges, applications needing some degree of ground truth can either manage
consistency themselves on a read or add a bolt-on service to manage the
consistency. For (2), if the client fails and stays down, all metadata
operations on the decoupled namespace are lost. If the client recovers, the
on-disk structures (for BatchFS and DeltaFS this is the SSTables used in
TableFS) can be recovered. In other words, the clients have state that cannot
be recovered if the node stays failed and any progress will be lost. This
scenario is a disaster for checkpoint-restart where missed cycles may cause the
checkpoint to bleed over into computation time. For (3), decoupled namespace
approaches sacrifice POSIX IO going as far as requiring the application to link
against the systems they want to talk to. In today's world of software defined
caching, this can be a problem for large data centers with many types and tiers
of storage. Despite well-known performance problems POSIX IO and REST are the
dominant APIs for data transfer.

>>>>

%% General
%The bottlenecks associated with accessing POSIX IO file system metadata are not
%limited to HPC workloads and the same challenges that plagued these systems for
%years are finding their way into the cloud. Workloads that deal with many small
%files ({\it e.g.}, log processing and database
%queries~\cite{thusoo:sigmod2010-facebook-infrastructure}) and large numbers of
%simultaneous clients ({\it e.g.}, MapReduce
%jobs~\cite{mckusick:acm2010-gfs-evolution}), are subject to the scalability of
%the metadata service. The biggest challenge is that whenever a file is touched
%the client must access the file's metadata and maintaining a file system
%namespace imposes small, frequent accesses on the underlying storage
%system~\cite{roselli:atec2000-FS-workloads}.  Unfortunately, scaling file
%system metadata is a well-known problem and solutions for scaling data IO do
%not work for metadata IO~\cite{roselli:atec2000-FS-workloads,
%abad:ucc2012-mimesis, alam:pdsw2011-metadata-scaling, weil:osdi2006-ceph}. 

@@

% Non POSIX IO
High performance computing has unique requirements for file systems and
well-defined workloads that make relaxing POSIX IO sensible.
BatchFS~\cite{zheng:pdsw2014-batchfs} assumes the application coordinates
accesses to the namespace, so the clients can batch local operations and merge
with a global namespace image lazily. Similarly,
DeltaFS~\cite{zheng:pdsw2015-deltafs} eliminates RPC traffic using subtree
snapshots for non-conflicting workloads and middleware for conflicting
workloads. MarFS~\cite{grider:pdsw2015-marfs} gives users the ability to lock
``project directories" and allocate clusters to demanding metadata
workloads.  Unfortunately, decoupling the namespace has costs: (1) merging
metadata state back into the global namespace is slow; (2) failures are local
to the failing node; and (3) the systems are not backwards compatible.

@@

For (1), state-of-the-art systems manage consistency in non-traditional ways:
IndexFS~\cite{ren:sc2014-indexfs} maintains the global namespace but blocks operations from other clients
until the first client drops the lease, BatchFS does operations on a snapshot
of the namespace and merges batches of operations into the global namespace,
and DeltaFS never merges back into the global namespace. The merging for
BatchFS is done by an auxiliary metadata server running on the client and
conflicts are resolved by the application. Although DeltaFS never explicitly
merges, applications needing some degree of ground truth can either manage
consistency themselves on a read or add a bolt-on service to manage the
consistency. For (2), if the client fails and stays down, all metadata
operations on the decoupled namespace are lost. If the client recovers, the
on-disk structures (for BatchFS and DeltaFS this is the SSTables used in
TableFS~\cite{ren:atc2013-tablefs}) can be recovered. In other words, the clients have state that cannot
be recovered if the node stays failed and any progress will be lost. This
scenario is a disaster for checkpoint-restart where missed cycles may cause the
checkpoint to bleed over into computation time. For (3), decoupled namespace
approaches sacrifice POSIX IO going as far as requiring the application to link
against the systems they want to talk to. In today's world of software defined
caching, this can be a problem for large data centers with many types and tiers
of storage. Despite well-known performance problems POSIX IO and REST are the
dominant APIs for data transfer.

### 2018-02-22 paper/sections/3_posix_overheads.tex
paper: camera ready template and squeeze to 10 pgs
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[tb] \centering
\includegraphics[width=1\linewidth]{./graphs/overhead-creates.png}
\caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/master/experiments/baseline-compile/visualize/viz.ipynb}{source}]
For the CephFS metadata server, create-heavy workloads ({\it e.g.},
\texttt{untar}) incur the highest disk, network, and CPU utilization because of
consistency/durability demands.}\label{fig:overhead-creates}
\end{figure}

@@

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.32\linewidth}
      \centering
      \includegraphics[width=1\linewidth]{graphs/slowdown-journal.png}
      \caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/master/experiments/baseline-durability/visualize/viz.ipynb}{source}]
      effect of journal} \label{fig:overhead-a}
  \end{subfigure}
  \begin{subfigure}[b]{.32\linewidth}
      \centering
      \includegraphics[width=0.98\linewidth]{graphs/slowdown-interfere-scale.png}
      \caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/master/experiments/baseline-creates/visualize/viz.ipynb}{source}]
      interference hurts variability}
      \label{fig:overhead-b}
  \end{subfigure}
  \begin{subfigure}[b]{.32\linewidth}
      \centering
      \includegraphics[width=1.15\linewidth]{graphs/behavior-interfere.png}
      \caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/master/experiments/baseline-interfere/visualize/viz.ipynb}{source}]
      interference increases RPCs}
      \label{fig:overhead-c}
  \end{subfigure}
  \caption{\newcomment{The durability and strong consistency slowdown of the
existing CephFS implementation increases as the number of clients scales.
Results in (a) and (b)  are normalized to 1 client that creates 100K files in
isolation.  (a) shows the effect of journaling metadata updates; ``segment(s)"
is the number of journal segments dispatched to disk at once. (b) shows the
slowdown when another client interferes by creating files in all directories
and (c) highlights the cause: }\oldcomment{The overhead of durability and
strong consistency in CephFS. (a) shows the effect of different journal segment
sizes, which are streamed into the object store for fault tolerance. (b) and
(c) show that} when another client interferes, capabilities are revoked and
metadata servers do more work.} \label{fig:overhead}
\end{figure*}

@@

% - sequential IO, trim redundant operations
\textbf{CephFS Design}: A journal of metadata updates that streams into the
resilient object store. Similar to LFS~\cite{rosenblum:acm1992-LFS} and
WAFL~\cite{hitz:wtec1994-WAFL} the metadata journal is designed to be large (on
the order of MBs) which ensures (1) sequential writes into the object store and
(2) the ability for daemons to trim redundant or irrelevant journal entries.
The journal is striped over objects where multiple journal updates can reside
on the same object. There are two tunables\newcomment{, related to groups of
journal events called segments,} for controlling the journal: the segment size
and the dispatch size ({\it i.e.} the number of segments that can be dispatched
at once).  Unless the journal saturates memory or CPU resources, larger values
for these tunables result in better performance.

>>>>

\begin{figure}[tb] \centering
\includegraphics[width=1\linewidth]{./graphs/overhead-creates.png}
\caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/master/experiments/baseline-compile/visualize/viz.ipynb}{source}]
For the CephFS metadata server, create-heavy workloads ({\it e.g.},
\texttt{untar}) incur the highest disk, network, and CPU utilization because of
consistency/durability demands.\vspace{-3ex}}\label{fig:overhead-creates}
\end{figure}

@@

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.32\linewidth}
      \centering
      \includegraphics[width=1\linewidth]{graphs/slowdown-journal.png}
      \caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/master/experiments/baseline-durability/visualize/viz.ipynb}{source}]
      effect of journal} \label{fig:overhead-a}
  \end{subfigure}
  \begin{subfigure}[b]{.32\linewidth}
      \centering
      \includegraphics[width=0.98\linewidth]{graphs/slowdown-interfere-scale.png}
      \caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/master/experiments/baseline-creates/visualize/viz.ipynb}{source}]
      interference hurts variability}
      \label{fig:overhead-b}
  \end{subfigure}
  \begin{subfigure}[b]{.32\linewidth}
      \centering
      \includegraphics[width=1.15\linewidth]{graphs/behavior-interfere.png}
      \caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/master/experiments/baseline-interfere/visualize/viz.ipynb}{source}]
      interference increases RPCs}
      \label{fig:overhead-c}
  \end{subfigure}
  \caption{\newcomment{The durability and strong consistency slowdown of the
existing CephFS implementation increases as the number of clients scales.
Results in (a) and (b)  are normalized to 1 client that creates 100K files in
isolation.  (a) shows the effect of journaling metadata updates; ``segment(s)"
is the number of journal segments dispatched to disk at once. (b) shows the
slowdown when another client interferes by creating files in all directories
and (c) highlights the cause: }\oldcomment{The overhead of durability and
strong consistency in CephFS. (a) shows the effect of different journal segment
sizes, which are streamed into the object store for fault tolerance. (b) and
(c) show that} when another client interferes, capabilities are revoked and
metadata servers do more work.\vspace{-3ex}} \label{fig:overhead}
\end{figure*}

@@

% - sequential IO, trim redundant operations
\textbf{CephFS Design}: A journal of metadata updates that streams into the
resilient object store. Similar to LFS~\cite{rosenblum:acm1992-LFS} 
the metadata journal is designed to be large (on
the order of MBs) which ensures (1) sequential writes into the object store and
(2) the ability for daemons to trim redundant or irrelevant journal entries.
The journal is striped over objects where multiple journal updates can reside
on the same object. There are two tunables\newcomment{, related to groups of
journal events called segments,} for controlling the journal: the segment size
and the dispatch size ({\it i.e.} the number of segments that can be dispatched
at once).  Unless the journal saturates memory or CPU resources, larger values
for these tunables result in better performance.

### 2018-02-22 paper/sections/4_methodology.tex
paper: camera ready template and squeeze to 10 pgs
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[tb]
\centering
%\includegraphics[width=50mm]{figures/fig-decouple.png}
\includegraphics[width=1.0\linewidth]{figures/fig-decouple.png}
\caption{Illustration of the \textbf{mechanisms} used by applications to build
consistency/durability semantics. Descriptions are provided by the
underlined words in Section~\S\ref{sec:the-cudelesfs-mechanisms}.
}\label{fig:decouple}
\end{figure}

@@

\begin{table}[t]
\begin{center}
\begin{tabular}{ l | l | l | l }
  C \(\rightarrow\) &&& \\  
  D \(\downarrow\)  	     & invisible         & weak        & strong  \\\hline
  none                       & append client journal            & append client journal          & RPCs    \\
                             &                   & +volatile apply &         \\\hdashline
  local                      & append client journal            & append client journal          & RPCs    \\
                             & +local persist    & +local persist  & +local  \\
                             &                   & +volatile apply &  persist\\\hdashline
  global                     & append client journal            & append client journal          & RPCs    \\
                             & +global persist   & +global persist & +stream \\
                             &                   & +volatile apply &         \\
\end{tabular}

\caption{Users can explore the consistency (C) and
durability (D) spectrum by composing Cudele mechanisms. 
\label{table:spectrum}}
\end{center}
\end{table}

>>>>

\begin{figure*}[tb]
  \centering
  \begin{subfigure}[b]{.32\linewidth}
    \centering
    \includegraphics[width=0.7\linewidth]{figures/fig-decouple0.png}
    \caption{Cudele \textbf{mechanisms}
    }\label{fig:decouple}
  \end{subfigure}
  \begin{subfigure}[b]{.32\linewidth}
    \centering
    \scalebox{0.7}{
    \begin{tabular}{ l | l | l | l }
      C \(\rightarrow\) &&& \\
      D \(\downarrow\)  & invisible             & weak                  & strong  \\\hline
      none              & append client journal & append client journal & RPCs    \\
                        &                       & +volatile apply       &         \\
                        &                       &                       &         \\\hdashline
      local             & append client journal & append client journal & RPCs    \\
                        & +local persist        & +local persist        & +local  \\
                        &                       & +volatile apply       & persist \\
                        &                       &                       &         \\\hdashline
      global            & append client journal & append client journal & RPCs    \\
                        & +global persist       & +global persist       & +stream \\
                        &                       & +volatile apply       &         \\
    \end{tabular}}
    \caption{building guarantees from mechanisms
    }\label{table:spectrum}
  \end{subfigure}
  \begin{subfigure}[b]{.32\linewidth}
    \includegraphics[width=1.0\linewidth]{graphs/composable-mechanisms.png}
    \caption{
    [\href{https://github.com/michaelsevilla/cudele-popper/blob/master/experiments/cudele-mechanisms/visualize/viz.ipynb}{source}]
    \textbf{mechanism} performance
    }\label{fig:composable-mechanisms}
  \end{subfigure}
  \caption{Cudele mechanism performance.
    (a) is an illustration of the \textbf{mechanisms} used by applications to build
    semantics. Descriptions are provided by the
    underlined words in Section~\S\ref{sec:the-cudelesfs-mechanisms}.
    (b) shows how users can explore the consistency (C) and
    durability (D) spectrum by composing Cudele mechanisms.
    \newcomment{(c) shows the overhead of processing 100K create events for each mechanism in
    \oldcomment{Table~\ref{table:mechanisms}}\newcomment{Figure~\ref{fig:decouple}},
    normalized to the runtime of writing events to client memory. The far right
    graph shows the cost of building real world systems.}
    \oldcomment{Performance of each mechanism (left) and building the
    consistency/durability semantics of real-world systems (right) for 100K files
    creates from a single client. Results are normalized to the runtime of writing
    events to the client's in-memory journal.}\vspace{-3ex}}
\end{figure*}

@@

### 2018-02-22 paper/sections/6_results.tex
paper: final revision for round 2
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>
paper: camera ready template and squeeze to 10 pgs
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Cudele lets \oldcomment{users}\newcomment{administrators} construct
consistency/durability guarantees using well-established research techniques
from other systems; so instead of evaluating the scalability and performance of
the techniques themselves against other file systems, we show that (1) the
mechanisms we propose are useful for constructing semantics used by real
systems and (2) the techniques can work side-by-side in the same
namespace for common use cases\oldcomment{, and (3) the combination of these techniques can help the
system scale further when subtrees are coupled to the correct type of
application}. \newcomment{These techniques have already proven to be effective
and scalable in systems that specialize an entire namespace according to a
single optimization strategy ({\it e.g.}, Lustre, BatchFS, DeltaFS).}
%, so our
%evaluation explores the behavior of the consistency/durability mechanisms and
%their effect with and without isolation.}

\newcomment{\indent We graph standard deviations for three runs (sometimes
error bars are too small to see) and normalize results to make our results more
generally applicable to different hardware. We use a CloudLab cluster of 34
nodes connected with 10Gbit ethernet, each with 16 2.4 GHz CPUs, 128GB RAM, and
400GB SSDs.  Each node uses Ubuntu 14.04 and we develop on Ceph's Jewel
release, version 10.2.1, which was released in May 2016. We use 1 monitor
daemon, 3 object storage daemons, 1 metadata server daemon, and up to 20
clients.}  We scope the evaluation to one metadata server and scale the number
of parallel clients \newcomment{each doing 100K operations because 100K is the
maximum recommended size of a directory in CephFS. We scale to 20 clients
because, as shown in Section~\S\ref{sec:posix-overheads}, 20 clients is enough
to saturate the resources of a single metadata server.} This type of analysis
shows the capacity and performance of a metadata server with superior metadata
protocols, which should be used to inform \oldcomment{load
balancing}\newcomment{metadata distribution} across a \oldcomment{metadata}
cluster. Load balancing across a cluster of metadata servers with partitioning
and replication can be explored with something like
Mantle~\cite{sevilla:sc15-mantle}.  \newcomment{To make our results
reproducible, this paper adheres to The Popper
Convention~\cite{jimenez_popper_2016} so experiments can be examined in more
detail, or even re-run, by visiting the \texttt{[source]} link next to each
figure.  The source code for Cudele is available on a branch~\cite{docs:cudele}
of our Ceph fork.}

@@

\subsection{Microbenchmarks}
\label{sec:microbenchmarks}
\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/composable-mechanisms.png}
\caption{
[\href{https://github.com/michaelsevilla/cudele-popper/blob/master/experiments/cudele-mechanisms/visualize/viz.ipynb}{source}]
\newcomment{Overhead of processing 100K create events for each mechanism in
\oldcomment{Table~\ref{table:mechanisms}}\newcomment{Figure~\ref{fig:decouple}},
normalized to the runtime of writing events to client memory. The far right
graph shows the overhead of building semantics of real world systems.}
\oldcomment{Performance of each mechanism (left) and building the
consistency/durability semantics of real-world systems (right) for 100K files
creates from a single client. Results are normalized to the runtime of writing
events to the client's in-memory journal.}\label{fig:composable-mechanisms}}
\end{figure}

@@

\begin{figure*}[tb]
  \centering
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/mergescale.png}
      \caption{
      [\href{https://github.com/michaelsevilla/cudele-popper/blob/master/experiments/cudele-mergescale/visualize/viz.ipynb}{source}]
      \newcomment{parallel creates on clients}
      }\label{fig:mergescale}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/block-allow.png}
      \caption{
      [\href{https://github.com/michaelsevilla/cudele-popper/blob/master/experiments/cudele-blockapi/visualize/viz.ipynb}{source}]
      \newcomment{block interference}
      }\label{fig:block-allow}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-sync.png}
      \caption{
      [\href{https://github.com/michaelsevilla/cudele-popper/blob/master/experiments/cudele-partialreads/visualize/viz.ipynb}{source}]
      \newcomment{syncing to global namespace}
      }\label{fig:slowdown-sync}
  \end{subfigure}
\caption{\oldcomment{ The performance and features of Cudele}\newcomment{Cudele
performance}. (a) \newcomment{shows the speedup of decoupled namespaces over
RPCs; \texttt{create} is the throughput of clients creating files in-parallel
and writing updates locally; \texttt{create+merge} includes the time to merge
updates at the metadata server. }\oldcomment{shows the cost of merging client
journals at the metadata server. Shipping and merging journals of
updates}\newcomment{Decoupled namespaces} scale better than RPCs because there
are less messages and consistency/durability code paths are bypassed. (b) shows
how the allow/block API isolates directories from interfering clients. (c) is
the slowdown of a single client syncing updates to the global namespace. The
inflection point is the trade-off of frequent updates vs. larger journal
files.}
\label{fig:use-cases}
\end{figure*}

@@

\oldcomment{Next we show how we can build application-specific subtrees by
composing mechanisms and that this approach of coupling well-established
techniques to specific applications results in a more a scalable global
namespace.} We start with clients creating files in private directories because
this workload is heavily studied in HPC~\cite{weil:sc2004-dyn-metadata,
ren:sc2014-indexfs, patil:fast2011-giga, zheng:pdsw2014-batchfs,
sevilla:sc15-mantle}, mostly due to checkpoint-restart~\cite{bent_plfs_2009}.
A more familiar example is uncompressing an archive ({\it e.g.}, \texttt{tar
xzf}), where the file system services a flash crowd of creates across all
directories as shown in Figure~\ref{fig:overhead-creates}.  But the workload
also appears in cloud workloads: Hadoop/Spark use the file \newcomment{system
to assign work units to workers and the performance is proportional to the
open/create throughput of the underlying file system~\cite{xiao:socc15-shardfs,
shi:vldb15-spark, shvachko:login2012-hdfs-scalability}; Big Data Benchmark jobs
examined in~\cite{chaimov:hpdc16-spark} have on the order of 15,000 file opens
or creates just to start a single Spark query and the Lustre system they tested
on did not handle creates well, showing up to a \(24\times\) slowdown compared
to other metadata operations. Common approaches to solve these types of
bottlenecks is to change the application behavior or to design a new file
system, like BatchFS or DeltaFS, that uses one set of metadata optimizations
for the entire namespace.} \oldcomment{ abstraction to exchange work units to
workers or to indicate when jobs complete  The workload is clients creating
100K files in private directories in the same global namespace.}

@@

Figure~\ref{fig:slowdown-sync} shows the performance degradation of a single
client writing \newcomment{1 million} updates to the decoupled namespace and
pausing to send updates to the metadata server. \oldcomment{The error bars are
the standard deviations of 3 runs.} We scale the namespace sync interval to
show the trade-off of frequently pausing or writing large logs of updates.  We
use an idle core to log the updates and to do the network transfer. The client
only pauses to fork off a background process, which is expensive as the address
space needs to be copied. The alternative is to pause the client completely and
write the update to disk but since this implementation is limited by the speed
of the disk, we choose the memory-to-memory copy of the fork approach.

As expected, syncing namespace updates too frequently has the highest overhead
(up to 9\% overhead if done every second). The optimal sync interval for
performance is 10 seconds, which only incurs 2\% overhead, because larger
intervals must write more updates to disk and network. For the 25 second
interval, the client only pauses 3-4 times but each sync writes about 278
thousand updates at once, which is a journal of size 678MB.

>>>>

Cudele lets \oldcomment{users}\newcomment{administrators} construct
consistency/durability guarantees using well-established research techniques
from other systems; so instead of evaluating the scalability and performance of
the techniques themselves against other file systems, we show that (1) the
mechanisms we propose are useful for constructing semantics used by real
systems and (2) the techniques can work side-by-side in the same
namespace for common use cases\oldcomment{, and (3) the combination of these techniques can help the
system scale further when subtrees are coupled to the correct type of
application}.
%\newcomment{These techniques have already proven to be effective
%and scalable in systems that specialize an entire namespace according to a
%single optimization strategy ({\it e.g.}, Lustre, BatchFS, DeltaFS).}
%, so our
%evaluation explores the behavior of the consistency/durability mechanisms and
%their effect with and without isolation.}

\newcomment{\indent We graph standard deviations for three runs (sometimes
error bars are too small to see) and normalize results to make our results more
generally applicable to different hardware. We use a CloudLab cluster of 34
nodes connected with 10Gbit ethernet, each with 16 2.4 GHz CPUs, 128GB RAM, and
400GB SSDs.  Each node uses Ubuntu 14.04 and we develop on Ceph's Jewel
release, version 10.2.1, which was released in May 2016. We use 1 monitor
daemon, 3 object storage daemons, 1 metadata server daemon, and up to 20
clients.}  We scope the evaluation to one metadata server and scale the number
of parallel clients \newcomment{each doing 100K operations because 100K is the
maximum recommended size of a directory in CephFS. We scale to 20 clients
because, as shown in Section~\S\ref{sec:posix-overheads}, 20 clients is enough
to saturate the resources of a single metadata server.} This type of analysis
shows the capacity and performance of a metadata server with superior metadata
protocols, which should be used to inform \oldcomment{load
balancing}\newcomment{metadata distribution} across a \oldcomment{metadata}
cluster. Load balancing across a cluster of metadata servers with partitioning
and replication can be explored with something like
Mantle~\cite{sevilla:sc15-mantle}.  \newcomment{To make our results
reproducible, this paper adheres to The Popper
Convention~\cite{jimenez:ipdpsw17-popper} so experiments can be examined in more
detail, or even re-run, by visiting the \texttt{[source]} link next to each
figure.  The source code for Cudele is available on a branch~\cite{docs:cudele}
of our Ceph fork.}

@@

\subsection{Microbenchmarks}
\label{sec:microbenchmarks}
%\begin{figure}[tb]
%\centering
%\includegraphics[width=1.0\linewidth]{graphs/composable-mechanisms.png}
%\caption{
%[\href{https://github.com/michaelsevilla/cudele-popper/blob/master/experiments/cudele-mechanisms/visualize/viz.ipynb}{source}]
%\newcomment{Overhead of processing 100K create events for each mechanism in
%\oldcomment{Table~\ref{table:mechanisms}}\newcomment{Figure~\ref{fig:decouple}},
%normalized to the runtime of writing events to client memory. The far right
%graph shows the overhead of building semantics of real world systems.}
%\oldcomment{Performance of each mechanism (left) and building the
%consistency/durability semantics of real-world systems (right) for 100K files
%creates from a single client. Results are normalized to the runtime of writing
%events to the client's in-memory journal.}\vspace{-3ex}\label{fig:composable-mechanisms}}
%\end{figure}

@@

\begin{figure*}[tb]
  \centering
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/mergescale.png}
      \caption{
      [\href{https://github.com/michaelsevilla/cudele-popper/blob/master/experiments/cudele-mergescale/visualize/viz.ipynb}{source}]
      \newcomment{parallel creates on clients}
      }\label{fig:mergescale}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/block-allow.png}
      \caption{
      [\href{https://github.com/michaelsevilla/cudele-popper/blob/master/experiments/cudele-blockapi/visualize/viz.ipynb}{source}]
      \newcomment{block interference}
      }\label{fig:block-allow}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-sync.png}
      \caption{
      [\href{https://github.com/michaelsevilla/cudele-popper/blob/master/experiments/cudele-partialreads/visualize/viz.ipynb}{source}]
      \newcomment{syncing to global namespace}
      }\label{fig:slowdown-sync}
  \end{subfigure}
\caption{\oldcomment{ The performance and features of Cudele}\newcomment{Cudele
performance}. (a) \newcomment{shows the speedup of decoupled namespaces over
RPCs; \texttt{create} is the throughput of clients creating files in-parallel
and writing updates locally; \texttt{create+merge} includes the time to merge
updates at the metadata server. }\oldcomment{shows the cost of merging client
journals at the metadata server. Shipping and merging journals of
updates}\newcomment{Decoupled namespaces} scale better than RPCs because there
are less messages and consistency/durability code paths are bypassed. (b) shows
how the allow/block API isolates directories from interfering clients. (c) is
the slowdown of a single client syncing updates to the global namespace. The
inflection point is the trade-off of frequent updates vs. larger journal
files.\vspace{-3ex}}
\label{fig:use-cases}
\end{figure*}

@@

\oldcomment{Next we show how we can build application-specific subtrees by
composing mechanisms and that this approach of coupling well-established
techniques to specific applications results in a more a scalable global
namespace.} We start with clients creating files in private directories because
this workload is heavily studied in HPC~\cite{weil:sc2004-dyn-metadata,
ren:sc2014-indexfs, patil:fast2011-giga, zheng:pdsw2014-batchfs,
sevilla:sc15-mantle}, mostly due to checkpoint-restart~\cite{bent_plfs_2009}.
A more familiar example is uncompressing an archive ({\it e.g.}, \texttt{tar
xzf}), where the file system services a flash crowd of creates across all
directories as shown in Figure~\ref{fig:overhead-creates}.  But the workload
also appears in cloud workloads: Hadoop/Spark use the file \newcomment{system
to assign work units to workers and the performance is proportional to the
open/create throughput of the underlying file system~\cite{shi:vldb15-spark}; Big Data Benchmark jobs
examined in~\cite{chaimov:hpdc16-spark} have on the order of 15,000 file opens
or creates just to start a single Spark query and the Lustre system they tested
on did not handle creates well, showing up to a \(24\times\) slowdown compared
to other metadata operations. Common approaches to solve these types of
bottlenecks is to change the application behavior or to design a new file
system, like BatchFS or DeltaFS, that uses one set of metadata optimizations
for the entire namespace.} \oldcomment{ abstraction to exchange work units to
workers or to indicate when jobs complete  The workload is clients creating
100K files in private directories in the same global namespace.}

@@

Figure~\ref{fig:slowdown-sync} shows the performance degradation of a single
client writing \newcomment{1 million} updates to the decoupled namespace and
pausing to send updates to the metadata server. \oldcomment{The error bars are
the standard deviations of 3 runs.} We scale the namespace sync interval to
show the trade-off of frequently pausing or writing large logs of updates.  We
use an idle core to log the updates and to do the network transfer. The client
only pauses to fork off a background process, which is expensive as the address
space needs to be copied.  As expected, syncing namespace updates too
frequently has the highest overhead (up to 9\% overhead if done every second).
The optimal sync interval for performance is 10 seconds, which only incurs 2\%
overhead, because larger intervals must write more updates to disk and network.
For the 25 second interval, the client only pauses 3-4 times but each sync
writes about 278 thousand updates at once, which is a journal of size 678MB.

%The alternative is to pause the client completely and
%write the update to disk but since this implementation is limited by the speed
%of the disk, we choose the memory-to-memory copy of the fork approach.
